### 2018-09-04 pilot_manuscript.Rmd
still working on the paper

```{r scraping, eval=FALSE, include=FALSE}
library(rvest)
####NY Times####
#Specifying the url for desired website to be scrapped
url <- 'https://www.nytimes.com/section/politics'

>>>>

```{r scraping, eval=FALSE, include=FALSE}

library(rvest)
####NY Times####
#Specifying the url for desired website to be scrapped
url <- 'https://www.nytimes.com/section/politics'
